---
title: "Functions of StatComp21068"
author: "Junfeng Zhao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Functions of StatComp21068}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## Overview

__StatComp21068__ is a simple R package developed to compute Coefficients of the unary linear regression equation by Gradient Descent approach with fixed step for the 'Statistical Computing' course.Three functions are considered, namely, _BGDR_ , _SGDR_ and _MBGDR_ .

The R package 'microbenchmark' can be used to benchmark the above R functions.


## Source R code

The source R code for _BGDR_ is as follows:


```{r, eval=FALSE}
BGDR <- function(x, y, theta, step, maxiter = 10000, epsilon = 1e-4){
    x1 <- as.matrix(x)
    m <- nrow(x1)
    x0 <- rep(1, m)
    X <- cbind(x0, x1)
    n <- ncol(X)
    beta <- matrix(theta, n, 1)
    iter <- 0
    
    while(iter < maxiter){
        grad <- t(X) %*% (X %*% beta - y) / m  
        beta_old <- beta
        beta <- beta - step * grad
        cost <- function(beta, X, y){
            return(sum((y - X %*% beta)^2)/(2 * m))
        }
        if(abs(cost(beta, X, y)-cost(beta_old, X, y)) < epsilon){
            break
        }
        iter <- iter + 1
    }
    beta <- as.numeric(beta)
    covariant <- c('x0', 'x1')
    result <- cbind(covariant, beta)
    return(result)
}
```


The source R code for _SGDR_ is as follows:


```{r, eval=FALSE}
SGDR <- function(x, y, theta, step, maxiter = 10000, epsilon = 1e-4){
    x1 <- as.matrix(x)
    m <- nrow(x1)
    x0 <- rep(1, m)
    X <- cbind(x0, x1)
    n <- ncol(X)
    beta <- matrix(theta, n, 1)
    iter <- k <- 0
    
    while(iter<maxiter){
        iter<-iter+1
        rand_i = ceiling(runif(1, 0, m))
        Xi <- t(X[rand_i,])
        yi <- y[rand_i]
        grad <- t((Xi %*% beta - yi) %*% Xi)
        beta_old <- beta
        beta <- beta - step * grad
        cost <- function(beta, X, y){
            return(sum((y - X %*% beta)^2)/(2 * m))
        }
        if(abs(cost(beta, X, y)-cost(beta_old, X, y)) < epsilon){
            break
        }
    }
    beta <- as.numeric(beta)
    covariant <- c('x0', 'x1')
    result <- cbind(covariant, beta)
    return(result)
}
```


The source R code for _MBGDR_ is as follows:


```{r, eval=FALSE}
MBGDR <- function(x, y, theta, step ,batch = 10, maxiter = 10000, epsilon = 1e-4){
    x1 <- as.matrix(x)
    m <- nrow(x1)
    x0 <- rep(1, m)
    X <- cbind(x0, x1)
    n <- ncol(X)
    beta <- matrix(theta, n, 1)
    size <- m %/% batch
    iter <- k <- 0
    while(iter<maxiter){
        iter<-iter+1
        group <- sample(1:m, size)
        Xb <- X[group, ]
        yb <- y[group]
        grad <- t(Xb) %*% (Xb %*% beta - yb) / size 
        beta_old <- beta
        beta <- beta - step * grad
        cost <- function(beta, X, y){
            return(sum((y - X %*% beta)^2)/(2 * m))
        }
        if(abs(cost(beta, X, y)-cost(beta_old, X, y)) < epsilon){
            break
        }
    }
    beta <- as.numeric(beta)
    covariant <- c('x0', 'x1')
    result <- cbind(covariant, beta)
    return(result)
}
```




## Example


The unary linear regression equation is $y_i=\beta_0+\beta_1x_{1i}$,I generates 5000 samples to compute Coefficients.


```{r}
library(StatComp21068)
library(microbenchmark)

n <- 5000
x <- runif(n, 0, 2)
y <- x * 4. + 5. + runif(n)
theta <- c(0,0)

BGDR(x, y, theta, 0.1)
SGDR(x, y, theta, 0.1)
MBGDR(x, y, theta, 0.1)

ts <- microbenchmark(MBGD=MBGDR(x, y, theta, 0.1),SGD=SGDR(x, y, theta, 0.1),BGD=BGDR(x, y, theta, 0.1))
summary(ts)[,c(1,3,5,6)]
```



```{r}
fit <- lm(y~x)
summary(fit)
```











